---
title: "Assessing the Replicability of Psychological Science Through Pedagogy"
short-title: "Replication Through Pedagogy"
output: kmr::apa_manuscript
csl: apa6.csl
bibliography: replication254.bib

document-params: "a4paper,man,apacite,floatsintext,longtable"

bib-tex: "replication254.bib"

author-information:
    - \author{Eric Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}

affiliation-information:
    - \affiliation{Department of Psychology, Stanford University}

author-note:
    "Thanks to the Stanford Department of Psychology and the Vice Provost for Undergraduate Education for funding to support the class."
    
abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct direct replications as part of their training; but to date there is limited evidence that this proposal can result in high-quality research outputs. We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course. The modal outcome was a partial replication, with most yielding weaker evidence than the original study. This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt. We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."
    
keywords:
    "Replication; Reproducibility; Pedagogy; Experimental Methods"
---

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(xtable)
library(readr)
library(tidyr)
library(ggplot2)
library(BayesFactor)
library(ggrepel)
#devtools::install_github("langcog/langcog")
library(langcog)
```

Reproducibility is a core value for empirical research, but there is increasing concern throughout psychology that weak statistical standards and methodological practices have led to low empirical rates of replication [@osc2015]. Under the current incentive structure for science, direct replication is not typically valued, however. One potential solution to this problem is to make direct replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea, however [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data -- beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] -- to support its efficacy. 

In the current article, we provide evidence on this issue by reporting the results of replication projects conducted in a single class (a graduate-level experimental methods course). As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies both give evidence about the state of replicability in the field and provide insight into the process of pedagogical replication. 

It is a challenging proposition to estimate the replicability of an entire literature [cf. @osc2015]. Making such an estimate requires determining a sampling strategy, a notion of what constitutes a direct replication, what constitutes a successful replication, among many other difficult decisions [@gilbert2016;@anderson2016]. In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work. We believe that this notion of whether a piece of research supports cumulative progress is an important construct. Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense. 

With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy. This process is dramatically facilitated by the use of standardized (and free) technical tools for statistical analysis, data and code sharing, and creation of web experiments. Nevertheless, there are significant limitations on what can be done in the course of a single term and within the constraints of a course budget. We return in the Discussion to limitations on our approach. 

In sum, we view the contribution of the current work to be two-fold. First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom. Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could easily be reproduced by a motivated student. 

```{r, results='asis'}
project_plan_raw <- read.csv("../data/planning_and_outcomes.csv")

project_plan <- project_plan_raw %>%
  filter(`include_in_final_writeup`==1) 

project_data_summary <- read_csv("../data/project_data_summary.csv")

d <- left_join(project_plan, project_data_summary, by = c("project_key"))
```

```{r}
ppt <- project_plan %>%
        select(cite, expt_num, open_data,
               open_materials, original_on_turk, original_n,collected_n)

names(ppt) = c("Citation", "Expt", "Data", "Materials", "Turk?", 
               "N (orig)","N (rep)")

# print(xtable(ppt, caption = "Summary of attempted replications", 
#        label = "tab:summary"), include.rownames=FALSE)
```

<!-- latex table generated in R 3.3.0 by xtable 1.8-2 package
 Fri Jun 24 12:02:11 2016 -->
\begin{table}[ht]
\footnotesize
\centering
\begin{tabular}{lllllrr}
  \hline
Citation & Expt & Data & Materials & Turk? & N (orig) & N (rep) \\ 
  \hline
Storm \& Stone (2015) & 3 & No & No & No &  48 &  61 \\ 
Lewis \& Oyserman (2015) & 4 & No & Yes & Yes & 122 & 128 \\ 
Scopelliti, Loewenstein, \& Vosgerau (2015) & 3 & No & Yes & Yes & 550 & 124 \\ 
Liverence \& Scholl (2015) & 1 & No & Some & No &  18 &  \\ 
Wang et al. (2015) & 2 & No & No & No & 219 & 397 \\ 
Sofer et al. (2015) & 1 & No & Yes & No &  48 &  95 \\ 
Ko, Sadler, \& Galinksy (2015) & 2 & Yes & Some & No &  40 &  40 \\ 
Atir, Rosenzweig, \& Dunning (2015) & 1b & No & Yes & Yes & 202 &  50 \\ 
Proudfoot, Kay, \& Koval (2015) & 1 & No & No & Yes &  80 &  84 \\ 
Zaval, Markowitz, \& Weber (2015) & 1 & Yes & Yes & Yes & 312 & 328 \\ 
Xu \& Franconeri (2015) & 1a & No & No & No &  12 &  27 \\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary of attempted replications.} 
\label{tab:summary}
\end{table}

# Methods

We begin by describing the general method of the class, then discuss shared methods for the replications and the process of development for each project.

## Class Outline

All projects were completed as part of a class (syllabus and materials available at [http://psych254.stanford.edu]()). At the initiation of class, all students were told that they had the opportunity to participate in a group replication project to which they could contribute their class project. The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup. 

Students selected projects based on interest, rather than via a systematic sampling strategy. Thus, all interpretation of our findings should be with respect to the distribution of student interest. Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general. This sampling strategy may thus bias our results towards more exciting or novel findings. A summary of the original findings is given in Table \ref{tab:summary}. 

## Participants

All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}. Note that of the `r nrow(ppt)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk. All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction." 

## Materials and Methods

Of the `r nrow(ppt)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available. For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors). Responses were received in all but one case, usually within a matter of days.  

## Workflow

All materials and methods for our replication studies are available at [https://github.com/StanfordPsych254](). All experiments were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis. 

One part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices. Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g. statistical tests, figures). This document can be compiled into a variety of formats (e.g., HTML, PDF, Microsoft Word). This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by copying and pasting between analysis outputs and manuscripts. 

## Preregistration and Review

To ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ES and RXDH). In addition to as-needed guidance, each student collected two pilot samples. The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students). The goal of this pilot was to ensure that all needed data were being logged by the experiment and that analytic scripts for the confirmatory analyses functioned appropriately. After pilot A was completed, the instructor or a TA reviewed the student's experiment (acting as a participant) and critiqued and reviewed the student's full analytic code and output. 

Once requested changes were made, the student conducted "Pilot B," using a handful of naive participants recruited from Mechanical Turk. The goal of this pilot was to ensure that participants were able to complete the experiment and did not report any substantial issues with instructions or technical details of the experiment. (All students were instructed to give participants a way to leave free-form comments at the end of the experiment but prior to debriefing text). At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analysis. The goal of this code review was to ensure that all planned analyses were specified correctly and with sufficient detail to permit inclusion in the broader analysis.

After Pilot B review was completed, students were given authorization to collect the full sample of participants, contingent on having made the requested change. Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework. In addition, prior to data collection, we pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).

## Sample size determination and statistical approach

After selecting a paper of interest, students selected a particular study from within that paper based on their judgment of interest and feasibility. The modal study chosen was the first, but several students chose later studies in a set as well. 

Despite the general emphasis in meta-analytic and reproducibility efforts to aggregate a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test in studies. Often a wide variety of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution. Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis.

Derermining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015]. Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially with the constraints of a limited budget -- it may be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or underpowered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered. 

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from pilot A sessions.] 
In 
`r sum(project_plan$power_standard == "80% power")`
cases, we powered the replication attempt to 80\% post-hoc power. In 
`r sum(project_plan$power_standard == "Original")` 
cases, we used the original sample size. In one case, the original experiment was apparently extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would apparently yield high power.  In one case, we reduced the number of trials as part of the adaptation to mechanical turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in Supplemntal Materials). 

## Individual Replications

Details of individual replications are available in the supplementary materials. Students chose findings from a wide variety of domains for replication. One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015]. A second cluster came from studies of social perception, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015]. Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].

# Results

## Pedagogical assessment 

Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and  2/3 projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product. (In one case, a student failed to complete the pre-registration but nevertheless submitted a pre-specified analysis plan to the instructors for review). 

The instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies. Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the modal rating was `r round(mean(d$replication_fidelity_MCF), digits = 2)`. Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might have an effect on the results. 

In two cases, in final review of the projects (after data collection), the instructor team decided that the student's choice of key statisical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases [@sofer2015;@proudfoot2015], the original authors had fit a multiple regression model to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research. 

## Confirmatory analyses

### Subjective judgments of replication

Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication. Criterion is based on the theoretical interpretation of the original finding. (0 = non-replication, .5 is substantial hints of the same pattern or a significant but different pattern, 1 = full replication). We find that the these ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students were `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.  

```{r}
d$high_fidelity <- d$replication_fidelity_MCF > median(d$replication_fidelity_MCF)
# table(d$replicated_TA,d$replicated_student) # Make prettier
#mean(d$replicated_team)

replicated <- d %>% 
  group_by(replicated_TA) %>%
  summarise(n= n()) %>%
  spread(replicated_TA, n) %>%
  mutate(measure = "replicated",
         value = "")

turk <- d %>% 
  group_by(original_on_turk, replicated_TA) %>%
  summarise(n= n()) %>%
  spread(replicated_TA, n) %>%
  rename(value = original_on_turk) %>%
  mutate(measure = "original on turk") 

fidelity <- d %>% 
  group_by(high_fidelity,replicated_TA) %>%
  summarise(n= n()) %>%
  spread(replicated_TA, n) %>%
  mutate(measure = "high fidelity") %>%
  rename(value = high_fidelity) %>%
  ungroup() %>%
  mutate(value = c("Yes","No")[as.numeric(value) + 1])

open_materials <- d %>% 
  group_by(open_materials,replicated_TA) %>%
  summarise(n= n()) %>%
  spread(replicated_TA, n) %>%
  mutate(measure = "open materials") %>%
  rename(value = open_materials)

outcomes <- bind_rows(replicated, turk, fidelity, open_materials) 
names(outcomes) <- c("No","Partial","Full", "Mediator","Value")
outcomes <- outcomes %>%
  select(Mediator, Value, No, Partial, Full)

# print(xtable(outcomes), include.rownames = FALSE)
```

\begin{table}[ht]
\centering
\begin{tabular}{llrrr|r}
  \hline
Mediator & Value & No & Partial & Full & Total\\ 
  \hline
Replicated? &  &   2 &   6 &   3 & 11 \\ 
\hline
  Original on turk & Yes &   1 &   2 &   2 & 5 \\ 
   & No &   1 &   4 &   1 & 6\\ 
\hline
  High fidelity replication? & Yes &   2 &   3 &   1  & 6\\ 
   & No &  &   3 &   2 & 5\\ 
\hline
  Open materials? & Yes &   1 &   3 &   1  & 4\\ 
   & Some &  &   1 &   1 & 2\\ 
   &  No &   1 &   2 &   1 & 4\\ 
\hline
\end{tabular}
\caption{\label{tab:results} Counts of instructor team replication ratings, split by various different mediating variables.}
\end{table}


The modal replication project in our sample was judged to be a "partial" replication, meaning that some aspects of the observed findings were different from those reported by the original authors. While this conclusion is dispiriting, it is also perhaps unsurprising given the complexity of the analyses reported in many of the original papers. In addition, `r sum(d$original_test=="interaction")` of the tests were interactions, which tend to have lower statistical power [@mcclelland1993] and have fared poorly in previous replication studies [@osc2015].

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically underpowered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if it was judged to be closer to the original:
`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
There were small numerical effects of being run on Mechanical Turk (
`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\%
vs. 
`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%. 
) and having open materials (
`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. 
`r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size. 

### Significance of the key effect size

We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level. Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value. The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective. 

```{r}
d$original_p_value_bins <- .1
d$original_p_value_bins[d$original_p_value %in% c("<.05","0.04")] <- "<.05"
d$original_p_value_bins[d$original_p_value %in% c("0.007","0.001")] <- "<.01"
d$original_p_value_bins[d$original_p_value %in% c("<.001","< .001")] <- "<.001"
d$rep_p_value_05 <- d$rep_p_value < .05

d$replicated_TA_factor <- factor(d$replicated_TA, levels = c(0, .5, 1), 
                                 labels = c("No","Partial","Yes"))
ggplot(d,aes(x=original_p_value_bins,y=rep_p_value, 
             color=d$replicated_TA_factor)) +
  geom_jitter(height=0, width=.2) +
  geom_hline(yintercept=c(0.05), lty = 2) + 
  geom_hline(yintercept=c(0.1), lty = 3) + 
  ylim(c(0,1)) +
  xlab("Original p-value (binned)") + 
  ylab("Replication p-value (exact)") + 
  theme_bw() + 
  scale_color_solarized(name = "Subjective replication rating") + 
  theme(legend.position = "bottom")
```

### Original ES in the confidence interval of the replication 

We determine whether the original reported effect size is included in the 95\% confidence interval found in the replication studies.  


```{r}
# Note that the sofer paper is off the charts (d > 16) and excluded
ggplot(d,aes(x=original_ES_d,y=rep_es, 
             color=d$replicated_TA_factor)) +
  geom_jitter(height=0, width=.2) +
  geom_vline(xintercept=c(0.2), lty = 5) +
  geom_vline(xintercept=c(0.5), lty = 2) +
  geom_vline(xintercept=c(0.8), lty = 3) +
  # geom_hline(yintercept=c(0.2), lty = 5) +
  # geom_hline(yintercept=c(0.5), lty = 2) +
  # geom_hline(yintercept=c(0.8), lty = 3) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  xlab("Original effect size (cohen's d)") + 
  ylab("Replication effect size (cohen's d)") + 
  theme_bw() + 
  scale_color_solarized(name = "Subjective replication rating") + 
  xlim(0, 4) +
  ylim(0, 4) +
  theme(legend.position = "bottom")

# Make beautiful ci chart here...

```


### Bayes factor analysis

Next, following @etz2016, we conducted a Bayesian analysis. 

```{r}
getBF <- function(t_stat, t_df) {
  return(ttest.tstat(t = t_stat, n1 = t_df, rscale = 1, simple = T))
};

tstatDF <- d %>%
  filter(original_t_stat != "NA") %>%
  select(project_key, replicated_TA_factor, first_author_name, original_t_stat, original_t_df, rep_t_stat, rep_t_df) %>%
  rowwise() %>%
  mutate(origBF = getBF(original_t_stat, original_t_df)) %>%
  rowwise() %>%
  mutate(repBF = getBF(rep_t_stat, rep_t_df), 
         df_ratio = rep_t_df/original_t_df)

tstatDF$origBF[7] <- 1e+11

ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = df_ratio, 
                             col = replicated_TA_factor)) +
  geom_abline(slope = 1, lty = 2) + 
  geom_smooth(method = "lm", se=FALSE) +
  # geom_smooth(data = filter(tstatDF,
  #                           !(first_author_name %in% c("Atir","Ko"))),
  #                           method = "lm", se=FALSE, lty = 2, size = .5) +
  geom_text_repel(aes(label = first_author_name), size = 3) +
  xlab("Original Bayes Factor") + 
  ylab("Replication Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1/3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c("1/10", "1/3", "3", "10","100", "1,000", 
                           "1,000,000","1,000,000,000")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1/3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c("1/10", "1/3", "3", "10","100", "1,000", 
                           "1,000,000","1,000,000,000")) + 
  scale_size_continuous(name = "Ratio of replication df to original df") + 
  scale_color_solarized(name = "Subjective replication rating") + 
  theme_bw() +
  theme(legend.position="bottom")

# note: fix slope on trend line, because the atir finding is a hack right now so it fits in the axes. 
```



<!-- Demographics -->




# Discussion

In this paper, we reported the results of a series of 11 direct replications of previously-published experiments from the 2015 volume of *Psychological Science*. We had two interlocking goals: first, to create a proof of concept for high-quality pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal. Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were disappointing. The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but results were not statistically significant and had both smaller effect size and lower evidential value than the originals. 

Our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project. While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources. Indeed, the majority of the projects in our report were relativley close replications and included the same or greater numbers of participants. Yet, despite these virtues, our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests. In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015]. What are the causes of this relatively low rate of replication? 

Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013,@ioannidis2005]. On the other hand, an alternative viewpoint is that -- especially for studies that leverage social constructs -- exact replication may be difficult across contexts [@gilbert2016;@vanbavel2016]. For both reasons of design and scale, our study here cannot disentangle these factors empirically. Nevertheless, the consistent descreases in effect size and evidential value we report seem consistent with a "winner's curse" -- that intial publications tend to over-estimate effects. And although our sample was too small for statistical inference, numerically our results do not support replication fidelity in terms of sample and procedure as a primary driver of success.

Our experiences performing and compiling the studies here sheds light on one further concern that we believe has been under-reported in past studies [including @osc2015]. Our standard model of replication is based on the notion of a single statistical test -- and its associated effect size -- being the key properties of a study that can be targeted for replication. Yet, as we mentioned above, selecting this key statistical test was difficult for most of the projects in our sample, and virtually impossible for some. We were often forced to consult other sections of the papers (e.g., abstracts, discussion sections) to gain clarity on what test was considered the critical one for the authors' interpretation. It is likely that some of our decisions would not be ratified by the original authors. 

Indeed, by the standards of clinical trials research, every single study we replicated in this report would be classified as exploratory research. No protocol was pre-registered, and the pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.  Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications. And in many cases, there are no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf. @bakeman2005]. This set of features -- which, in our experience, are endemic to published psychological work -- makes replication research within the conventional statistical paradigm extremely challenging. 

In our view, two recommendations will improve this situation dramatically. First, pre-registration typically requires the selection of one or a small number of statistical analyses to be designated as critical for interpretation. Were this information available, it would have simplified the problem of selecting effects to replicate in several cases. Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here, in a number of ways. In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archving data and analytic code is often critical for other investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is a way of allowing more flexible reuse. 

In conclusion, our results here demonstrate the practical possibility of performing replication research in the classroom. There are many challenges for ensuring high-quality replications in a pedagogical setting -- from checking experimental methods to reviewing analytic code for errors -- but we would argue that these are not just pedagogical challenges. They are challenges for psychological science. We believe that the openness and transparency we pursued here as part of our pedagogical goals should be models not just for other classes but for future research more broadly. 

# Supplemental Materials: Project-By-Project Methods Addendum


```{r, fig.height=9, fig.width=6}
# library(png)
# layout(matrix(1:24,nr=6,byr=T))
# for (key in project_plan$project_key) {
#   orig <- readPNG(paste0("../figures/",key,"-original.png"))
#   rep <- readPNG(paste0("../figures/",key,"-replication.png"))
# 
#   par(mai=c(0,0,0,0))
#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
#   rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)
# 
#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
#   rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)
# 
# }
```

For each project, we present a summary of the finding, the key statistical test, and the outcomes of the replication. Side-by-side visualizations are presented in Figure SM1. 

## Sofer et al. (2015)

- key statistic in original 



# References 





<!-- # Supplemental -->

<!-- All materials that are needed for class to implement -->
<!-- Email templates -->
<!-- Spreadsheets -->
<!-- TA/prof auditing processes -->